\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb}
% more math
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsbsy}
%\usepackage{dtklogos}

\usepackage{color}
\newcommand{\mt}[1]{\marginpar{\small #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% new commands
\newcommand{\nc}{\newcommand}
% operators
\renewcommand{\div}{\vec{\nabla}\! \cdot \!}
\newcommand{\grad}{\vec{\nabla}}
% latex shortcuts
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bal}{\begin{align}}
\newcommand{\eali}{\end{align}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
% DGFEM commands
\newcommand{\jmp}[1]{[\![#1]\!]}                     % jump
\newcommand{\mvl}[1]{\{\!\!\{#1\}\!\!\}}             % mean value
\newcommand{\keff}{\ensuremath{k_{\textit{eff}}}\xspace}
% shortcut for domain notation
\newcommand{\D}{\mathcal{D}}
% vector shortcuts
\newcommand{\vo}{\vec{\Omega}}
\newcommand{\vr}{\vec{r}}
\newcommand{\vn}{\vec{n}}
\newcommand{\vnk}{\vec{\mathbf{n}}}
\newcommand{\vj}{\vec{J}}
% extra space
\newcommand{\qq}{\quad\quad}
% common reference commands
\newcommand{\eqt}[1]{Eq.~(\ref{#1})}                     % equation
\newcommand{\fig}[1]{Fig.~\ref{#1}}                      % figure
\newcommand{\tbl}[1]{Table~\ref{#1}}                     % table

\newcommand{\ud}{\,\mathrm{d}}

\newcommand{\tcr}[1]{\textcolor{red}{#1}}
\newcommand{\tcb}[1]{\textcolor{blue}{#1}}
\newcommand{\tcg}[1]{\textcolor{green}{#1}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\bibliographystyle{elsarticle-num}
\begin{center}
{ \Large Answers to Reviewer \#2}
\end{center}

\bigskip

\noindent Ms. Ref. No.: JOMP-D-15-00204\\
Title: ``Viscous Regularization for the Non-equilibrium Seven-Equation Two-Phase Flow Model', \\
{\it Springer Journal of Scientific Computing}\\

%\bigskip
%
%In {\color{blue}blue} are reviewer's comments, in black are our answers, in {\color{red}red} are Jean's comments,
%and in {\color{green}green} are Marco's comments.
%
\bigskip

{\color{blue}
After the recent work by Guermond and Popov where a general class of viscous
regularizations of compressible Euler equations is investigated, the present work
proposes an extension in the case of the non-equilibrium seven-equation two-
phase flow model. To address such an issue, the authors introduce a general
viscosity within the adopted model. Then, they derive the entropy evolution
law, now perturbed by the additional viscosity. By adopting a relevant defini-
tion of the additional viscosity terms, the authors claim that a minimum entropy
principle is satisfied. This study is completed by a chapman-Enskog extension
to get the associated five-equation model in the limit of infinite relaxation co-
efficients. The analysis is achieved by considering the incompressible regime
governed by low Mach number. The authors claim that the adopted viscosity
regularization does not modify the required incompressible regime. Finally, nu-
merical illustrations are displayed in order to attempt to illustrate the relevance
of the viscosity regularizations.

My opinion about this work is not good at all since this paper looks like a poor
extension of the work by Guermond and Popov.}

We disagree with your assessment. This paper deals with a regularization of a two-pressure and two-velocity
two-phase flow model of the Baer and Nunziato type. These models are strictly hyperbolic 
non-conservative system of equations (HNCSE); hyperbolicity being an important property with respect to
causality principle. However, this type of system involves many difficulties 
for the derivation of numerical methods, often rendering the Riemann problem determination complex due 
to the 7 waves presents (in 1D, more in multi-D). We have provided an alternative 
numerical method, based on an artificial viscosity principle, and we believe this is a valuable alternative for the
solution of such hyperbolic systems. As such, declaring that our work is a 
poor extension of the work by Guermond and Popov is not correct. Furthermore, in the revised
manuscript, we clarify many aspects related to hyperbolic non-conservative system of equations and  
use an entropy condition following the theory developed by Del Maso-Le Floch-Mariat (DLM). 
The DLM theory extends the classical definitions of a weak solution and the entropy solution
(see paragraphs 2 \& 3 of the introduction and the new section 3.1.)

\bigskip


{\color{blue}
1. The main point of this work concerns the derivation of the minimum
entropy principle. Here, the establishment of this property is not clear
at all. I think that the proof is incomplete. For instance, Guermond
and Popov need (and prove) the positiveness of the density. I think that
the positiveness of partial density is here needed but no proof is given.
Moreover, I am convinced that $\alpha_k \in [0, 1]$ is also necessary and must be
proved. I urge the author to read carefully the paper by Guermond and
Popov and reconsider the establishment of their results.}

We did read the paper by Guermond and Popov. We agree with you that proof of the positiveness of the partial density was missing and we added it (section 3.4).
We also performed the same work for the volume fraction equation. In both cases, the viscous terms are required in order to prove positiveness of the
partial density and to show that the volume fraction remains bounded within the interval [0,1].

%\tcr{we can cite Guermond for the phasic regularized continuity equation and show
%than $\alpha \rho$ is non-negative. Then we can work on the alpha equations (both of them) to show
%that  $\alpha_k \in [0, 1]$. From this, we conclude that $\rho_k$ is non-negative.} \tcg{Showing that $\alpha \rho$ is
%non-negative is trivial based on Guermond's work. Showing, however, that $\rho$ is non-negative seems trickier.}
\bigskip


{\color{blue}
2. Several times, thew author speak about uniqueness of the numerical solution
. I don’t understand the meaning of these words. Moreover, this
paper does not contains numerical derivations. Page 7, the authors refer
to Leveque (pages 27-28 in Numerical Methods for Conservation Laws),
but these two pages in the leveque’s book coincides with the introduction
of weak solutions and entropy inequalities. Nothing about uniqueness of
the numerical solution.}

We meant 'convergence of the numerical solution to the weak entropy solution' and not 'uniqueness of the numerical solution'. We corrected it throughout the paper.
We also removed the reference to Leveque's book that is not the most appropriate here as you noticed and replaced it with a more extensive paragraph in section 3.1 that refers to
the DLM theory (section 3.1).

%\tcr{Using Leveque for everything is a mistake. We will correct this using
%piece of the answer we gave to reviewer \#1} \tcg{Once again, 'entropy solution' and
%not 'uniqueness of the weak solution'.}
\bigskip


{\color{blue}
3. The numerical schemes, used to get the numerical illustrations, are not
specified. However, the derivation of a numerical scheme to approximate
the weak solution of the model under consideration is a very difficult task.}

A short paragraph explaining our space/time discretization was present but we unfortunately deleted it by mistake
in the version that was submitted. We apologize for this. It has been added back (first portion of section 5). 
All simulations are carried out using continuous finite elements.

\bigskip


{\color{blue}
4. The presentation of the entropy residual is absolutely not relevant. In
section 3.2, I understand the opportunity to omit the underlined terms.
However, the equation (15) turns out to be wrong. The authors have to
introduce a specific notation to designate the entropy residual.}

We disagree. The sign of the entropy equation, which is function of the entropy residual, is used as an entropy condition for non-conservative and conservative system of equations in order to ensure
convergence of the numerical solution to a weak entropy solution [15, 19]. We double checked equation (15) and believe it is right. It is used in section 3.4 to show that the entropy residual remains positive with the proper
viscous regularization. We added a specific notation to designate the entropy residual, as you requested, to readability.  

%\tcr{This is where the reviewer really shows he doesn't get it} \tcg{We can still add 
%a specific notation for the entropy residual as he requested it.}
\bigskip


%{\color{blue}
%In addition, I think that these results are not suitable to be published in Journal
%of Scientific Computing. As a consequence, I do not recommend the publication
%of this work.}
%
%\tcr{Pure BS}
\bigskip


\end{document}

